Supplementary Materials

### 2025-07-07 manuscript.Rmd
Start modifying tables

We piloted a three-armed cluster randomised controlled trial [@GerdinWärnberg2022]. There were a standard care arm and two intervention arms, ATLS^®^ and PTC training. We collected data for four months in all three arms, first during a one month observation phase and then during a three month intervention phase (or continued observation in the standard care arm). We included the one month lead to be able to evaluate the feasibility of comparing patient outcomes both as absolute differences between the intervention phases, and as differences in change from baseline. In the published protocol, we also aimed to estimate probable effect sizes and other measures needed for the sample size calculations of a full-scale trial [@GerdinWärnberg2022], but we revised this aim in the light of current guidance on the conduct and reporting of pilot trials [ADD CITATION].

@@

During the course of this pilot study we deviated from the protocol in several ways. We have reported these deviations where appropriate in the methods section, and provide a list as Supplementary
material S1. The most important deviation was the revision of the aim of this pilot study, because we initially planned to estimate potential effect sizes and other measures to help sample size calculations for a full scale trial, in addition to the feasibility outcomes. However, current guidance advice against using pilot studies to estimate effect sizes, as the usefulness of these estimates is questionable [INSERT REF]. We therefore decided to only report patient outcomes descriptively. Another important deviation from the protocol was the training of emergency medicine residents. We initially planned to train only surgical residents, but trauma management routines varied between participating hospitals, and we decided to adapt to local routines. The full scale study will need to accommodate this variation as part of the protocol.

>>>>

We piloted a three-armed cluster randomised controlled trial [@GerdinWärnberg2022]. There were a standard care arm and two intervention arms, ATLS^®^ and PTC training. We collected data for four months in all three arms, first during a one month observation phase and then during a three month intervention phase (or continued observation in the standard care arm). We included the one month lead to be able to evaluate the feasibility of comparing patient outcomes both as absolute differences between the intervention phases, and as differences in change from baseline. In the published protocol, we also aimed to estimate probable effect sizes and other measures needed for the sample size calculations of a full-scale trial [@GerdinWärnberg2022], but we revised this aim in the light of current guidance on the conduct and reporting of pilot trials [@teresi_guidelines_2022].

@@

During the course of this pilot study we deviated from the protocol in several ways. We have reported these deviations where appropriate in the methods section, and provide a list as Supplementary
material S1. The most important deviation was the revision of the aim of this pilot study, because we initially planned to estimate potential effect sizes and other measures to help sample size calculations for a full scale trial, in addition to the feasibility outcomes. However, current guidance advice against using pilot studies to estimate effect sizes, as the usefulness of these estimates is questionable [@eldridge_how_2015; @teresi_guidelines_2022]. We therefore decided to only report patient outcomes descriptively. Another important deviation from the protocol was the training of emergency medicine residents. We initially planned to train only surgical residents, but trauma management routines varied between participating hospitals, and we decided to adapt to local routines. The full scale study will need to accommodate this variation as part of the protocol.

### 2025-07-07 supplementary-materials.Rmd
Start modifying tables

| Cluster                                                       | City       | Beds | Type    | Study period | 
+---------------------------------------------------------------+------------+------+---------+--------------+
| Dr R N Cooper Municipal General Hospital                      | Mumbai     |      | Public  |              |
| Seth GS Medical College and KEM Hospital                      | Mumbai     |      | Public  |              |
| Lokmanya Tilak Municipal Medical College and General Hospital | Mumbai     |      | Public  |              |
| MEDICA Superspeciality Hospital                               | Kolkata    |      | Private |              |
| Medical College                                               | Kolkata    |      | Public  |              |
| Nilratan Sircar Medical College & Hospital                    | Kolkata    |      | Public  |              |
| Postgraduate Institute of Medical Education and Research      | Chandigarh |      | Public  |              |
+---------------------------------------------------------------+------------+------+---------+--------------+

>>>>

| Cluster                                                       | City       | Beds | Type    | Study period | 
+---------------------------------------------------------------+------------+------+---------+--------------+
| Dr R N Cooper Municipal General Hospital                      | Mumbai     | 600  | Public  |              |
| Seth GS Medical College and KEM Hospital                      | Mumbai     | 1800 | Public  |              |
| Lokmanya Tilak Municipal Medical College and General Hospital | Mumbai     | 1850 | Public  |              |
| MEDICA Superspeciality Hospital                               | Kolkata    | 300  | Private |              |
| Medical College                                               | Kolkata    | ??   | Public  |              |
| Nilratan Sircar Medical College & Hospital                    | Kolkata    | 1910 | Public  |              |
| Postgraduate Institute of Medical Education and Research      | Chandigarh | 1400 | Public  |              |
+---------------------------------------------------------------+------------+------+---------+--------------+
